Analyses

### 2024-07-24 src/analysis/Analysis.Rmd
last cleanups in analysis files

## Exploration
```{r "exploration", fig.height=7, fig.width=8}
source(here("src/analysis/exploration.R"))
p_b1
p_b2
p_e1a
p_e1b
```

```{r "explore-profiles", fig.height=7, fig.width=8}
source(here("src/analysis/profiles.R"))
prof1 
prof2
```

```{r "explor2", eval=FALSE}
source(here("src/analysis/profile_resp.R"))
kbl(e1_nlp, booktabs =T, caption = "\\label{tab:conditions}Profile Dutch Stance Annotators") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "7cm") %>%
  column_spec(2, width = "7cm")

>>>>

## Exploration
```{r "exploration", fig.height=7, fig.width=8}
source(here("src/analysis/exploration.R"))
p_b1
p_b2
p_e1a
p_e1b
p_e1c
```

```{r "explore-profiles", fig.height=10, fig.width=15}
source(here("src/analysis/profiles.R"))
prof1 
prof2
```

```{r "explor2", eval=FALSE, echo=FALSE}
source(here("src/analysis/profile_resp.R"))
kbl(e1_nlp, booktabs =T, caption = "\\label{tab:conditions}Profile Dutch Stance Annotators") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "7cm") %>%
  column_spec(2, width = "7cm")
